Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Rephrasing

\section{Experiments}
We test the CGPCM by applying it to synthetic and real-world signals. We show that in certain situations the causality constraint provides a useful inductive bias that leads to better predictions.

@@

Finally, note that in nearly every case predictions through the SMF approximation have better calibrated credible regions than predictions through the MF approximation.
% \subsection{Speech}
% Coming up.

>>>>

\section{Experiments}
We test the CGPCM by applying it to synthetic and real-world signals. We show that in certain situations the causality constraint provides an useful inductive bias that leads to better predictions.

@@

Finally, note that the SMF approximation consistently has better calibrated credible regions compared to the MF approximation. For example, in the filter $h$, kernel $k_{f\cond h}$, PSD of $f \cond h$ of the CGPCM in \cref{fig:toy_causal_sample}, the MF approximation fails to capture the truth in its credible region, whereas the SMF approximation does capture the truth.
% \subsection{Speech}
% Coming up.
